---
title       : Data products
subtitle    : Exploring CO2 dataset 
author      : Andrew Sila, Data Science course learner
job         : Nairobi, Kenya
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Exploring CO2 dataset

1. View the data 
2. Using a boxplot
3. Anova

--- .class #id 

====
## View data
1. Start by reading in the CO2 dataset
2. Give the number of observation to be viewed in th header.
3. We set six as the default number to view in the app.
```{r,echo=TRUE}
data(CO2)
head(CO2)
```

--- .class #id 

===

## Boxplot
1. Visualize the CO2 dataset with a boxplot
2. Plant co2 uptake can be viewed versus: Type, Treatment and conc 

```{r,echo=TRUE}
data(CO2)
with(CO2, boxplot(uptake~conc,col="blue",ylab="Co2 uptake",xlab="conc"))
```

--- .class #id 

===

## Anova

Test for significance of each of the three experiment factors:
    1. Type
    2. Treatment
    3. conc

### Testing for conc illustrated.
```{r,echo=TRUE}
data(CO2)
with(CO2, aov(uptake~conc))
```




